Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-16 tex/paper1/paper1.tex
adding in normality tests
edits to the paper

\shorttitle{Properties of coronal Fourier power spectra}
\shortauthors{Ireland et al.}

@@

\title{Properties of coronal Fourier power spectra and their
  implications for coronal seismology and solar atmospheric heating.}

@@

\author{J. Ireland}
\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
  20771, USA.}

@@

\author{A. R. Inglis}
\affil{Catholic University of America / NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
  20771, USA.}

@@

\section{Observations}\label{sec:obs}
Data was obtained from SDO-AIA using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data at 12 second cadence was selected in the 171\AA
and 193\AA\ wavebands (2012-09-23 00:00 - 06:00 UT, 1800 images per
waveband).  These wavebands were selected in order to obtain a wide
range of approximate temperatures in the solar corona.

The downloaded cutout data was prepared for analysis using the
SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
move the downloaded level 1.0 FITS files to level 1.5 FITS files.  All
further processing from this point was performed in the SunPy 0.4
(http://www.sunpy.org) data analysis environment.  Images were
de-rotated to compensate for solar rotation, based on the center of
the field of view of each image.  After de-rotation, each image layer
was co-registered with the image half way through the dataset, at
approximately 03:00 UT.

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.}
\label{fig:loc171193}
\end{figure}

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - \langle I(t)
\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects in the
\PS.  Figures \ref{fig:compare171193} show example power
spectra, plotted using a log-log scale, from a single location inside
each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a \PL\ at lower frequencies, and flattens out at higher
frequencies.

>>>>

\shorttitle{Coronal Fourier power spectra}
\shortauthors{Ireland et al.}

@@

\title{Coronal Fourier power spectra: implications for coronal
  seismology and coronal heating.}

@@

\author{J. Ireland}
\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1, Greenbelt, MD
  20771, USA.}

@@

\author{A. R. Inglis}
\affil{NASA Goddard Space Flight Center, Greenbelt, MC. 671.1, MD, 20771, USA.
\affil{Physics Department, The Catholic University of America, Washington, DC, 20664, USA.}

@@

\section{Observations}\label{sec:obs}

The data used in this study is from the Atmospheric Imaging Assembly
(AIA) \cite{2012SoPh..275...17L} on board the Solar Dynamics
Observatory (SDO) \cite{2012SoPh..275....3P}.  AIA observes in
multiple wavebands simultaneously and continuously, at high cadence
(12 seconds) and at high spatial resolution (0.6 arcseconds per pixel
at the Sun).  These data enable detailed comparisons between phenomena
seen in multiple wavebands, and are therefore ideal for assessing the
frequency content of the solar atmosphere.  The data was acquired
using the Lockheed Martin Solar Astrophysics cutout service
(http://lmsal.com/get\_aia\_data/).  Six hours of image data in the
time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
in the 171\AA and 193\AA\ wavebands is used.  These wavebands were
selected because previous studies in similar wavebands (TRACE 171\AA
and 193\AA) show the presence of coronal oscillations.  The cutout of
the Sun selected covers two adjacent $\beta\gamma$ regions NOAA AR
11575 and AR 11577.  This cutout was selected for two reasons.  First,
it is quiescent in that there were no X-ray flares or other
large-scale disturbances over the spatial extent of the cutout within
the time range.  Therefore, any variations in the plasma properties
cannot be ascribed to large-scale disturbances.  Second, the selected
cutout region contains a sunspot, and sunspots are known to be
locations over which three minute oscillations have been detected by
other instruments \citep{2002A&A...387L..13D}.

The downloaded cutout data was prepared for analysis using the
SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
convert the downloaded level 1.0 FITS cutout files to level 1.5 FITS
files.  This involves translating, scaling and rotating the images so
they have the same sun-center, image scale with solar north in the
same direction.  All further processing from this point was performed
in the SunPy 0.4 (http://www.sunpy.org) data analysis environment.
Images were de-rotated to compensate for solar rotation, based on the
center of the field of view of each image.  After de-rotation, each
image layer was co-registered with the image half way through the
dataset, at approximately 03:00 UT.

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is ??? to ??? in the x-direction, and ??? - ??? in the
  y-direction, in heliocentric cartesian co-ordinates
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - \langle I(t)
\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects in the
\PS.  The full 12 second cadence is used, yielding time series of 1800
samples.  The full spatial resolution is also retained in order to
obtain fine detail on the variation of frequency content as a function
of location.  Figures \ref{fig:compare171193} show example power
spectra, plotted using a log-log scale, from a single location inside
each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a \PL\ at lower frequencies, and flattens out at higher
frequencies.
